The 2018 heatwave and its implications on ozone induced damage on vegetation in a subarctic climate

### 2020-09-15 VegOzone.tex
Conclusion and plots.
Remove Aud from list of authors.
Fixed location of Pallas which had been wrong.

\Author[1]{Stefanie}{Falk}
\Author[2]{Ane Victoria}{Vollsnes}
\Author[3]{Lisa}{Emberson}
\Author[3]{Connie}{O'Neill}
\Author[2]{Aud Else}{Berglen Eriksen}
%\Author[1]{Bj{\o}rg}{Rognerud}
\Author[1]{Frode}{Stordal}
\Author[1]{Terje}{Koren Berntsen}

@@

\copyrightstatement{TEXT}

@@

\begin{table}[t]
  \caption{Past and present ozone observation sites in northern Fennoscandia. Data available on \href{http://ebas.nilu.no/}{EBAS}.}
  \label{tab:ebas_obs}
  \begin{tabular}{lllllrl}
    \tophline
    Name       & Country & ID      & \multicolumn{3}{c}{Location} & Operational\\
    &         &         & lat             & lon               & alt            &\\
    &         &         & (\unit{^\circ N}) & (\unit{^\circ E})  & (\unit{m})     &\\
    \middlehline
    Esrange    & SWE     & SE0013R & 67.83           & 21.07             & 475            & 1991 -- present\\
    Janiskoski & RUS     & RU0001R & 68.93           & 28.85             & 118            & 1995 -- 1997\\
    Jergul     & NOR     & NO0030R & 69.45           & 24.60             & 255            & 1997 -- 2011\\
    Karasjok   & NOR     & NO0055R & 69.467          & 25.217            & 333            & 1988 -- 1997\\
    Pallas     & FIN     & FI0096G & 69.97           & 24.12             & 565            & 1995 -- present\\
    Svanvik    & NOR     & NO0047R & 69.45           & 30.03             & 30             & 1986 -- 1996$^\dagger$\\
    \bottomhline
  \end{tabular}
  \belowtable{$^\dagger$ Exclusive ozone monitoring growing seasons 2018/19 operated by NILU.} % Table Footnotes
\end{table}

>>>>

\Author[1]{Stefanie}{Falk}
\Author[2]{Ane Victoria}{Vollsnes}
\Author[3]{Lisa}{Emberson}
\Author[3]{Connie}{O'Neill}
%\Author[2]{Aud Else}{Berglen Eriksen}
%\Author[1]{Bj{\o}rg}{Rognerud}
\Author[1]{Frode}{Stordal}
\Author[1]{Terje}{Koren Berntsen}

@@

%\copyrightstatement{TEXT}

@@

\begin{table}[t]
  \caption{Past and present ozone observation sites in northern Fennoscandia. Data available on \href{http://ebas.nilu.no/}{EBAS}.}
  \label{tab:ebas_obs}
  \begin{tabular}{lllllrl}
    \tophline
    Name       & Country & ID      & \multicolumn{3}{c}{Location} & Operational\\
    &         &         & lat             & lon               & alt            &\\
    &         &         & (\unit{^\circ N}) & (\unit{^\circ E})  & (\unit{m})     &\\
    \middlehline
    Esrange    & SWE     & SE0013R & 67.83           & 21.07             & 475            & 1991 -- present\\
    Janiskoski & RUS     & RU0001R & 68.93           & 28.85             & 118            & 1995 -- 1997\\
    Jergul     & NOR     & NO0030R & 69.45           & 24.60             & 255            & 1997 -- 2011\\
    Karasjok   & NOR     & NO0055R & 69.467          & 25.217            & 333            & 1988 -- 1997\\
    Pallas     & FIN     & FI0096G & 67.97           & 24.12             & 565            & 1995 -- present\\
    Svanvik    & NOR     & NO0047R & 69.45           & 30.03             & 30             & 1986 -- 1996$^\dagger$\\
    \bottomhline
  \end{tabular}
  \belowtable{$^\dagger$ Exclusive ozone monitoring growing seasons 2018/19 operated by NILU.} % Table Footnotes
\end{table}
